### 2024-07-17 Article/Article-english.tex
typo

Now for any algebraic subgroup $H \subseteq (\mathbb{C}^\times)^n$ we defined \textit{the~identity component} $H^\circ$
as a~connected component containing an~identity element of the~group $H$. It follows from theorem~3
that $\Pi(H^\circ) = 1$. Thus, the~following statements are proved.

>>>>

Now for any algebraic subgroup $H \subseteq (\mathbb{C}^\times)^n$ we define \textit{the~identity component} $H^\circ$
as a~connected component containing an~identity element of the~group $H$. It follows from theorem~3
that $\Pi(H^\circ) = 1$. Thus, the~following statements are proved.
